Assignment 1

### 2005-01-19 classes/semantics/assn1.tex
formatting change

To prove this, simply consider the typing rules for application and abstraction, which
shows that the abstraction must have type $t \rightarrow t'$, and therefore
$e_1 : t'$ and $e_2 : t$, from the typing of the application.  Thus we
can apply our lemma to obtain the desired conclusion.

>>>>

\begin{proof}
To prove this, simply consider the typing rules for application and abstraction, which
shows that the abstraction must have type $t \rightarrow t'$, and therefore
$e_1 : t'$ and $e_2 : t$, from the typing of the application.  Thus we
can apply our lemma to obtain the desired conclusion.
\end{proof}
